Staged Abstract Interpreters

### 2018-10-19 paper/10_intro.tex
continue working on outline
draft on contribution

2. whole-program analysis is slow, how to optimize it systematically/mechanically?
bridging the gap between designing sound analyses and implementing efficient analyses.

@@

>>>>

2. precise whole-program analysis can be very slow, how to optimize it systematically/mechanically?
bridging the gap between designing sound analyses and implementing efficient analyses.

@@

\begin{itemize}
\item Starting from a definitional abstract interpreter for a higher-order functional language,
  we show how to turn it into a staged abstract interpreter by adding stage annotations with 
  Lightweight Modular Staging (LMS) framework. We later extend the abstract interpreter to support
  imperative language features, such as states, loops and exceptions.
\item We elaborate the idea that the staged abstract interpreter not only improves the performance 
  but also the scalability, which are two major issues in static analysis, if we apply it on open
  programs. TODO: more on this point.
\item To evaluate the generality of the idea, we conduct several case studies. 
  First we revisited Abstract Compilation (TODO: cite), which is a closure generation technique applied 
  on 0-CFA and can be understood as an instance of staged abstract interpreter. 
  Second, we demonstrate existing control-flow analysis techniques, such as context/flow/path-sensitive 
  analysis and store-widening can be integrated with staged abstract interpreters.
  Finally, we show it also can be applied to numerical analysis in an imperative language.
  (Optional: taint/information flow analysis?)
\item We also emprically evaluate the performance improved of staged abstract interpreter with the 
  unstaged version and other existing optimizations on benchmarks.
\end{itemize}
